---
title: "Fiche de synthèse des données CARHYCE sur la station `r params$station`"
author: "OFB DR Occitanie"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
    toc_float: TRUE
params:
  station: '05061942'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE}
load(file="../output/testgraphique.Rdata")
```

## LA STATION
```{r,echo=FALSE}
nom_station<-ma_station$SME_LB_STATION_MESURE_EAUX_SURFACE
code_station<-ma_station$SME_CD_STATION_MESURE_EAUX_SURFACE
departement_station<-ma_station$SME_CD_DEPARTEMENT
```
**Nom** : `r nom_station`  
**Code SANDRE** : `r code_station`  
**Département** : `r departement_station`  
**HER** :   
**Réseau** :   
Photo : comment la récupérer ?  
Vue aérienne : *idem*    


## L'OPERATION
```{r,echo=FALSE}
date_operation<-ma_station$OPE_DATE_REALISATION
id_operation<-ma_station$OPE_ID
longueur_ope<-ma_station$OPE_LR
```
**Date** : `r date_operation`  
**Identifiant opération** : `r id_operation`  
**Longueur station (m)** : `r longueur_ope`  


BLBALBLBLBLBLA


## QUELQUES GRAPHIQUES

You can also embed plots, for example:

```{r, echo=FALSE}
plot(pressure)
```

```{r}
plot(graphique3)
```
```{r stat tableau transect, echo=FALSE}
summary(transect2)
```
```{r,echo = FALSE}
knitr::kable(nb_ope,
             caption="nombre d'opération par an")
```
```{r}
flextable::flextable(nb_ope)
```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
